---
title: "HOMEWORK 2 - Creating Value Through Data Mining (S402010)"
author: "Liam Phan"
date: "`r Sys.Date()`"
output:
  rmdformats::material :
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: true
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls()) # clean environment
```

# <span style="color: #1c6155;">Quick Start</span> 

## Loading Packages

```{r 2, warning=FALSE, message=FALSE }

library(data.table) # Efficient Dataframe 
library(lubridate) # For Dates 
library(tidyverse) # Multiple Package for Useful Data wrangling
library(esquisse) # Intuitive plotting
library(plyr) # Data splitting
library(ggplot2) # Plot Graphs
library(naniar) # for NA exploration in Dataframe
library(sp) # spatial data
library(plotly) # Make ggplot2 Dynamic
library(gissr) # Spatial Transformations
library(leaflet) # For Map
library(leaflet.providers) # For Custom Icons
library(geosphere) # Spatial Calculations
library(DT) # Render Table in a explorable UI
library(gridExtra) # Multiple Plot at once
library(corrplot) # Correlation Plot
library(RColorBrewer) # For Color Palette
library(rmdformats) # Theme of HTML
library(manipulateWidget) # Handling multiple plotly graphs

```

> Those are required packages



# <span style="color: #1c6155;">Exercise 1.</span> 

## 5.6 Evaluating Predictive Performance

### a. 

> If the company beings working with a new set of 1000 leads to sell the same services, similar to the 500 in the plot study, witout any use of predictive modeling to target sales efforts, what is the estimated profit? 

### b.

> If the firm wants the average profit on each sale to at least double the sales effort cost, and applies an appopriate cutoff with this predictive model to a new set of 1000 leads, how far down the new list of 1000 should it proceed (how many deciles)?

### c.

> Still considering the new list of 1000 leads, if the company applies this predictive model with a lower cutoff of $2500, how far should it proceed down the ranked leads, in terms of deciles?

### d. 

> Why use this two-stage process for predicting sales--why not simply develop a model for predicting profit for the 1000 new leads?

# <span style="color: #1c6155;">Exercise 2.</span> 


# <span style="color: #1c6155;">Exercise 3.</span>



# <span style="color: #1c6155;">References</span>

[Github Repo for this Homework 2](https://github.com/LiamPhan17/DATA_MINING_HW2)

[Data Mining for Business Analytics: Concepts, Techniques, and Applications in R](https://www.wiley.com/en-us/Data+Mining+for+Business+Analytics:+Concepts,+Techniques,+and+Applications+in+R-p-9781118879368)